### 2012-04-06 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: Corrections and final(?) additions.

\section{On Inference of XML Schema with the Knowledge of an Obsolete One}
The aim of approach described in \cite{Mlynkova:2009:IXS:1862681.1862693} is to exploit an obsolete XML schema as an additional input information to infer a new schema more efficiently. An XML schema can become obsolete due to changes in a set of XML documents, without capturing these changes in the schema. Thus, the schema becomes outdated and according to the paper, this case is quite common.

@@

In the second step, regular expressions from the corrected schema are specialized with regard to the XML documents, resulting in a more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simplier form, if this transcription preserves the validity, and refactorization to improve readability.

>>>>

\section[On Inference of XML Schema with the Knowledge of an Obs. One]{On Inference of XML Schema with the Knowledge of an Obsolete One}
The aim of approach described in \cite{Mlynkova:2009:IXS:1862681.1862693} is to exploit an obsolete XML schema as an additional input information to infer a new schema more efficiently. An XML schema can become obsolete due to changes in a set of XML documents, without capturing these changes in the schema. Thus, the schema becomes outdated and according to the paper, this case is quite common.

@@

In the second step, regular expressions from the corrected schema are specialized with regard to the XML documents, resulting in a more precise and readable schema. Optional substeps are pruning of unused schema fragments, correction of lower and upper bounds of occurrences, transcription of operators to a more restrictive but simpler form, if this transcription preserves the validity, and refactorization to improve readability.

### 2012-04-06 doc/theses/mikula/experiments.tex
Master thesis: Corrections and final(?) additions.

\begin{table}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\end{tabular}
\caption{Inferred type statements.}
\label{TAB_inferred_types}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & 0.417 \\ \hline
\end{tabular}
\caption{Inferred key statements.}
\label{TAB_inferred_keys}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.417 \\ \hline
\end{tabular}
\caption{Key statements inferred from the extended test data.}
\label{TAB_inferred_keys_2}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.333 \\ \hline
\end{tabular}
\caption[Key statements inferred using the modified JP3 statements.]{Key statements inferred from the extended test data using the modified JP3 statements.}
\label{TAB_inferred_keys_3}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{decimal} \\ \hline
\texttt{/site/people/person/profile/gender} $\rightarrow$ \texttt{string} \\ \hline
\end{tabular}
\caption{Inferred type statements B.}
\label{TAB_inferred_types_b}
\end{table}

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site//item, {@id})} & 0.333 \\ \hline
\texttt{(/site/people/person, {@id})} & 0.6 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, {buyer/@person})} & -0.6 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, {itemref/@item})} & -0.917 \\ \hline
\texttt{(/site/regions/europe/item, {@id})} & 0.6 \\ \hline
\end{tabular}
\caption{Inferred key statements B.}
\label{TAB_inferred_keys_b}
\end{table}

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Node} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person/profile/interest/@category)} & 1 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction/itemref/@item)} & 1 \\ \hline
\texttt{(/site/people/person/profile/gender)} & 0.9 \\ \hline
\end{tabular}
\caption{Inferred negative uniqueness statements B.}
\label{TAB_inferred_negative_uniqueness_statements_b}
\end{table}

>>>>

\begin{table}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\end{tabular}
\caption{Inferred type statements A}
\label{TAB_inferred_types}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & 0.417 \\ \hline
\end{tabular}
\caption{Inferred key statements A}
\label{TAB_inferred_keys}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.417 \\ \hline
\end{tabular}
\caption{Key statements inferred from the extended test data A}
\label{TAB_inferred_keys_2}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.333 \\ \hline
\end{tabular}
\caption[Key statements inferred using the modified JP3 statements]{Key statements inferred from the extended test data using the modified JP3 statements}
\label{TAB_inferred_keys_3}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{decimal} \\ \hline
\texttt{/site/people/person/profile/gender} $\rightarrow$ \texttt{string} \\ \hline
\end{tabular}
\caption{Inferred type statements B}
\label{TAB_inferred_types_b}
\end{table}

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site//item, {@id})} & 0.333 \\ \hline
\texttt{(/site/people/person, {@id})} & 0.6 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, {buyer/@person})} & -0.6 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, {itemref/@item})} & -0.917 \\ \hline
\texttt{(/site/regions/europe/item, {@id})} & 0.6 \\ \hline
\end{tabular}
\caption{Inferred key statements B}
\label{TAB_inferred_keys_b}
\end{table}

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Node} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person/profile/interest/@category)} & 1 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction/itemref/@item)} & 1 \\ \hline
\texttt{(/site/people/person/profile/gender)} & 0.9 \\ \hline
\end{tabular}
\caption{Inferred negative uniqueness statements B}
\label{TAB_inferred_negative_uniqueness_statements_b}
\end{table}
